The Galactic Midplane Is Not a Plane: Implications for Dynamical Analysis with \textit{Gaia} Data and Beyond

### 2019-05-21 paper/ms.tex
Update keywords order
Add link to repo

\keywords{Milky Way disk -- Milky Way evolution -- Milky Way dynamics --
Galaxy structure -- Orbits -- Stellar dynamics}

@@

>>>>

\keywords{Milky Way disk -- Milky Way dynamics -- Milky Way evolution --
Galaxy structure -- Orbits -- Stellar dynamics}

@@

\subsection*{Supplementary Material}
All code used in this work is available at:
\url{https://github.com/gusbeane/actions_systematic}.
